Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-11-08 tables/stormseverity.tex
Work some more on draft

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Tue Oct  8 14:03:24 2019
\begin{table}[ht]
\centering
\caption{Summary statistics for the number of county tropical cyclone exposures under each metric.     
	 The median and interquartile range of number of county exposures per tropical cyclone are based on
         the tropical cyclones for which at least one US county was exposed. The years for which
         data are available for each metric are given in Table 1.} 
\label{tab:exposuresummaries}
\begin{tabular}{p{1.75cm}p{3cm}p{4cm}p{4cm}}
  \toprule
Metric & Mean (interquartile range) of county exposures per year & Median (interquartile range) of county exposures per tropical cyclone & Tropical cyclone with most counties exposures (\# exposed counties) \\ 
  \midrule
Rain & 401 (152, 553) & 68 (14, 146) & Frances, 2004 (464) \\ 
  Wind & 143 (51, 232) & 25 (14, 58) & Ike, 2008 (251) \\ 
  Flood & 213 (84, 248) & 26 (6, 58) & Ivan, 2004 (318) \\ 
  Tornado & 53 (16, 43) & 7 (2, 16) & Ivan, 2004 (91) \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Nov  8 11:15:53 2019
\begin{table}[ht]
\centering
\caption{Summary statistics for the number of county tropical cyclone exposures under each metric.} 
\label{tab:exposuresummaries}
\begin{tabular}{p{4.5cm}p{4.5cm}p{4.5cm}}
  \toprule
Metric (years available) & Mean (interquartile range) of county exposures per year & Tropical cyclone with most counties exposures (\# exposed counties) \\ 
  \midrule
Distance (1988--2015) & 433 (224, 503) & Beryl, 1994 (330) \\ 
  Rain (1988--2015) & 401 (152, 553) & Frances, 2004 (464) \\ 
  Wind (1988--2011) & 143 (51, 232) & Ike, 2008 (251) \\ 
  Flood (1996--2015) & 213 (84, 248) & Ivan, 2004 (318) \\ 
  Tornado (1996--2015) & 53 (16, 43) & Ivan, 2004 (91) \\ 
   \bottomrule
\end{tabular}
\end{table}

### 2019-11-08 writing/ehp_abstract.tex
Work some more on draft

\noindent \textbf{Background:} Tropical cyclones bring severe impacts to
	\ac{US} communities, including substantial human health risks, from
	hazards that include wind, rain, flooding, and tornadoes. However, 
	it is difficult to conduct multi-year, multi-storm epidemologic 
	studies without storm hazard datasets that can easily be linked to 
	human health data. Further, while some storm exposure metrics are
	straightforward to measure (e.g., distance from a community to a 
	storm's track), they may poorly capture exposure to storm hazards. \\ 
\textbf{Objectives:} (1)~Provide an open-source dataset to improve tropical
	cyclone exposure assessment for health-related research and
	(2)~investigate agreement between county-level assessments of tropical cyclone
	exposure when based on different storm hazards, to clarify 
	risk of exposure misclassification in epidemiologic studies. \\ 
\textbf{Methods:} We created an open-source dataset with county-level data on
	exposure to tropical cyclones in the \ac{US}. The dataset includes
	measures of distance from the storm track, maximum sustained wind,
	rainfall, flooding, and tornadoes for all land-falling or near-land
	Atlantic basin storms over multiple years (1996\,--\,2011 for all
	metrics, up to~1988\,--\,2015 for specific metrics). [Validation] We measured
	agreement in county-level exposure assessment for all pairwise
	combinations of these metrics. \\ 
\textbf{Results:} We created an open-source dataset ... 
	[Most data agreed well. Flooding is hard to measure.]
	In most of the storms investigated, agreement in county-level
	exposure assessment was at best moderate, and often poor, when using
	distance compared with four hazard-based measurements. There was also
	substantial disagreement in exposure assessment based on all pairwise
	combinations of the four hazard-based measurements. There were
	geographic patterns in exposures based on these metrics, with most
	wind-based exposures near the coast, flood- and rain-based exposures
	extending to inland and northern counties, and tornado-based exposures
	in southern counties. \\ 
\textbf{Discussion:} Our results provide a multi-hazard dataset that can be
	leveraged for epidemiologic research on tropical cyclones.  Further,
	our results suggest that when epidemiologic studies use distance as a
	surrogate for tropical cyclone exposure, or use one hazard-based metric
	when the impact is partly or fully caused by a different hazard, the
	study will be prone to exposure misclassification.  
\end{abstract}

>>>>

\noindent \textbf{Background:} Tropical cyclones bring severe impacts to
	\ac{US} communities, including substantial human health risks, from
	hazards that include wind, rain, flooding, and tornadoes. However, 
	it is difficult to conduct multi-year, multi-storm epidemologic 
	studies without storm hazard datasets that can easily be linked to 
	human health data. Further, while some storm exposure metrics are
	straightforward to measure (e.g., distance from a community to a 
	storm's track), they may poorly capture exposure to storm hazards. \\ 
\textbf{Objectives:} (1)~Provide an open-source dataset to improve tropical
	cyclone exposure assessment for health-related research and
	(2)~investigate patterns and agreement between county-level assessments of tropical cyclone
	exposure when based on different storm hazards, to inform the design of tropical cyclone epidemiological studies. \\ 
\textbf{Methods:} We created an open-source dataset with county-level data on
	exposure to tropical cyclones in the \ac{US}. The dataset includes
	measures of distance from the storm track, maximum sustained wind,
	rainfall, flooding, and tornadoes for all land-falling or near-land
	Atlantic basin storms over multiple years (1996\,--\,2011 for all
	metrics, up to~1988\,--\,2015 for specific metrics). We compared these
	measurements to other potential data sources and investigated patterns
	and agreement among binary exposure classifications based on these
	metrics across multiple years and counties. \\ 
\textbf{Results:} Here, we created and shared a large-scale dataset with 
	consistent and comprehensive measurements of county-level exposure
	to storm hazards. These data typically 
	agreed with data from other sources, although there are some caveats
	that should be considered by potential users. Long-term geographic patterns in binary 
	classifications based on these data agree with previous results from
	atmospheric science. County-level exposure classification for a storm differs substantially 
	depending on the hazard metric used. \\ 
\textbf{Discussion:} Our results provide a multi-hazard dataset that can be
	leveraged for epidemiologic research on tropical cyclones.  Further,	
	our results suggest that epidemiologic studies that use distance as a
	surrogate for tropical cyclone exposure, or use one hazard-based metric
	when the impact is partly or fully caused by a different hazard, will 
	likely be prone to exposure misclassification.  
\end{abstract}

### 2019-11-08 writing/ehp_discussion.tex
Work some more on draft

Tropical cyclone wind exposures had a strong coastal pattern, which is
consistent with the dramatic decrease in wind intensity that typically
characterizes the landfall of tropical cyclones.  Tropical cyclone rain
exposures tended to extended further inland compared to wind exposures, up to
the Appalachian mountains. This agrees with previous research indicating that
the Appalachian mountains' topography both enhances precipitation during
tropical cyclones and provides hydrological conditions for severe
flooding~\parencite{rees2001}.  Almost all tropical cyclone tornado exposures
were in southern coastal states, consistent with previous evidence that most
noteworthy tropical cyclone-related tornadoes occur on the right-side of the
tropical cyclone track in Atlantic-basin \ac{US} storms~\parencite{moore2012}.
The exposure averages we calculated are somewhat limited as estimates of
long-term frequencies, as tropical cyclones follow decadal
patterns~\parencite{kossin2007more} likely not adequately captured in the
available data, which covered less than 20 years. However, exposure assessments
spanning over a century have found similar patterns for distance- and
wind-based metrics~\textcite{zandbergen2009, kruk2010} \textbf{[double-check
that refs found similar patterns]}.

@@

This suggests that the use of a distance-based metric to assess exposure to any
of these hazards, or the use of measurements from one hazard as a proxy for
exposure to any of the other hazards considered, would often be problematic,
introducing exposure misclassification. \textbf{[Compare with Grabich results?]}
For some studies, such exposure misclassification might plausibly be
differential (i.e., associated with the outcome of interest or with factors
associated with risk of the outcome of interest).  For example, tropical
cyclone wind exposures tend to be concentrated in counties near the coast,
while tropical cyclone wind exposures sometimes extend well inland.  If the
etiologically-relevant exposure for a health outcome is extreme rainfall but
exposure is classified based on measurements of wind, the probability of being
misclassified as unexposed would be higher in inland counties, while the
probability of being misclassified as exposed would be higher in coastal
counties. If coastal counties differ from inland counties in either the outcome
of interest or in factors associated with risk of that outcome, exposure
misclassification would be differential~\parencite{savitz2016interpreting}.
Such differential exposure misclassification could bias estimates of tropical
cyclone effects either towards the null (estimating a lower or null association
compared to the true association that exists) or away from the null (estimating
a larger association than actually exists)~\parencite{savitz2016interpreting,
armstrong1998effect}.

@@

The dataset presented here does have several limitations, in addition to the
caveats previously discussed. First, the dataset is not comprehensive of all
possible tropical cyclone hazards. For example, coastal counties can experience
dangerous storm surge, which is not specifically covered in this dataset
(although some resulting flooding would be captured). We are exploring ways to
include this in future versions of the dataset, although to date we have
focused on exposures that could affect any county, whether inland or coastal.
Second, this data is aggregated to the county level. Many health outcome
datasets are aggregated at this level, but some may be aggregated at a finer
spatial resolution (e.g., Census tract or ZIP code). We have published the wind
model we used to create this dataset as its own open-source R package
\parencite{stormwindmodel}, and this model can be used to model
storm-associated winds at a finer spatial resolution; however, measurements of
other hazards cannot similarly be re-scaled through tools we provide. Finally,
we provide these data and associated software tools through R packages, and so
some experience in the R programming language is required to make full use of
them. However, R is currently a popular programming language for environmental
epidemiology, allowing the data to reach a large audience, and we are exploring
options to create a web application using the Shiny platform to allow more
user-friendly web-based access of the data \parencite{shiny2019}.

@@

To conduct epidemiological studies that span multiple communities and tropical 
cyclones, it is critical to have consistent and comprehensive measurements of 
community-level exposure to hazards of the storm. Here we have created and 
shared a dataset that provides these data for counties in the United States
over multiple years. Despite some limitations in this dataset, it provides 
a powerful tool for expanding tropical cyclone epidemiology studies to more
extensively leverage existing administrative and vital data, allowing researchers
to improve our understanding of how these storms affect community-wide risk of 
numerous health outcomes, including outcomes that are also common outside of storm 
periods and so may be hard to attribute on a case-by-case basis to a storm. 
Further, this dataset provides hazard measurements that are comparable across
communities and storms, which allows epidemiological researchers to design studies
to explore how health risks are modified by characteristics of both the storms and
the communities that are hit. The data are given in an open-source format, along 
with associated software tools, which allows them to be freely used and for others
to explore all associated code and to contribute additions through platforms like 
GitHub.

>>>>

Tropical cyclone wind exposures had a strong coastal pattern, which is
consistent with the dramatic decrease in wind intensity that typically
characterizes the landfall of tropical cyclones.  Tropical cyclone rain
exposures tended to extended further inland compared to wind exposures, up to
the Appalachian mountains. This agrees with previous research indicating that
the Appalachian mountains' topography both enhances precipitation during
tropical cyclones and provides hydrological conditions for severe
flooding~\parencite{rees2001}.  Almost all tropical cyclone tornado exposures
were in southern coastal states, consistent with previous evidence that most
noteworthy tropical cyclone-related tornadoes occur on the right-side of the
tropical cyclone track in Atlantic-basin \ac{US} storms~\parencite{moore2012}.
The exposure averages we calculated are somewhat limited as estimates of
long-term frequencies, as tropical cyclones follow decadal
patterns~\parencite{kossin2007more} likely not adequately captured in the
available data, which covered less than 20 years. However, exposure assessments
spanning over a century have found similar patterns for distance- and
wind-based metrics~\parencite{zandbergen2009, kruk2010}

@@

This suggests that the use of a distance-based metric to assess exposure to any
of these hazards, or the use of measurements from one hazard as a proxy for
exposure to any of the other hazards considered, would often be problematic,
introducing exposure misclassification. This result reinforces similar findings
for a study of Florida's 2004 storm season on methods of measuring exposure to
tropical cyclones for epidemiological
research~\parencite{grabich2015measuring}.  For some studies, such exposure
misclassification might plausibly be differential (i.e., associated with the
outcome of interest or with factors associated with risk of the outcome of
interest).  For example, tropical cyclone wind exposures tend to be
concentrated in counties near the coast, while tropical cyclone wind exposures
sometimes extend well inland.  If the etiologically-relevant exposure for a
health outcome is extreme rainfall but exposure is classified based on
measurements of wind, the probability of being misclassified as unexposed would
be higher in inland counties, while the probability of being misclassified as
exposed would be higher in coastal counties. If coastal counties differ from
inland counties in either the outcome of interest or in factors associated with
risk of that outcome, exposure misclassification would be
differential~\parencite{savitz2016interpreting}.  Such differential exposure
misclassification could bias estimates of tropical cyclone effects either
towards the null (estimating a lower or null association compared to the true
association that exists) or away from the null (estimating a larger association
than actually exists)~\parencite{savitz2016interpreting, armstrong1998effect}.

@@

The dataset presented here does have several limitations, in addition to the
caveats previously discussed. First, the dataset is not comprehensive of all
possible tropical cyclone hazards. For example, coastal counties can experience
dangerous storm surge, which is not specifically covered in this dataset
(although some resulting flooding would be captured). We are exploring ways to
include this in future versions of the dataset, although to date we have
focused on exposures that could affect any county, whether inland or coastal.
Second, this data is aggregated to the county level. Many health outcome
datasets are aggregated at this level, but some may be aggregated at a finer
spatial resolution (e.g., Census tract or ZIP code). We have published the wind
model we used to create this dataset as its own open-source R package
\parencite{stormwindmodel}, and this model can be used to model
storm-associated winds at a finer spatial resolution; however, measurements of
other hazards cannot similarly be re-scaled through tools we provide. Next,
we provide these data and associated software tools through R packages, and so
some experience in the R programming language is required to make full use of
them. However, R is currently a popular programming language for environmental
epidemiology, allowing the data to reach a large audience, and we are exploring
options to create a web application using the Shiny platform to allow more
user-friendly web-based access of the data \parencite{shiny2019}. 
Finally, to assess patterns and agreement for binary exposure classifications, 
we have chosen one set of sensible thresholds for binary classifications based
on continuous metrics (rainfall, maximum sustained winds, and distance from 
the storm's track). Results and conclusions would differ somewhat with other
threshold choices. We have published all our code for this analysis online
[web address], in case other researchers would like to explore other 
threshold choices for these analyses.

@@

To conduct tropical cyclone epidemiological studies that span multiple
communities and storms, it is critical to have consistent and comprehensive
measurements of county-level exposure to storm hazards. Here we have created
and shared a dataset that provides these data for counties in the United States
over multiple years. Despite some limitations in these data, they provide a
powerful tool for expanding tropical cyclone epidemiology studies to more
extensively leverage existing administrative and vital data, allowing
researchers to investigate how these storms affect community-wide risk of
numerous health outcomes, including outcomes that are also common outside of
storm periods and so may be hard to identify through traditional disaster
surveillance.  Further, this dataset provides hazard measurements that are
comparable across communities and storms, which allows epidemiological
researchers to design studies to explore how health risks are modified by
characteristics of both the storms and the communities that are hit. The data
are given in an open-source format, along with associated software tools, which
allows them to be freely used and for others to explore all associated code and
to contribute additions through platforms like GitHub.

### 2019-11-08 writing/ehp_introduction.tex
Work some more on draft

Here, we describe how we developed this dataset and explore how its
measurements compare to other data that could be used to characterize tropical
cyclone hazards in the context of epidemiological research. \textit{Further, we expand
on previous research that found large differences in which communities are
assessed as exposed to a tropical cyclone depending on whether exposure
assessment is based on distance to the storm's track or if it uses a metric
incorporating storm-related winds within the county during the storm,
concluding that a study may be prone to bias from exposure misclassification if
distance to the storm track is used as a proxy measurement for exposure
assessment~\parencite{grabich2015measuring}.}  The previous study investigated
this question for one hurricane season in Florida. Here we expand to
investigate this question across all counties in states in the eastern half of
the \ac{US} over multiple storms and years.  Further, we investigate patterns
in exposure classification based on other metrics of storm-related
hazards---rainfall, flooding, and tornadoes---that are important to characterize to
improve understanding of the inland health impacts of tropical
cyclones~\parencite{czajkowski2011, moore2012}. These results can help
epidemiologists design studies and plan statistical analysis for
multi-year, multi-community studies that investigate changes in community-wide
rates of health outcomes during exposure to the hazards brought by tropical
cyclones, including counties inland from a storm's landfall.

>>>>

Here, we describe how we developed this dataset and explore how its
measurements compare to other data that could be used to characterize tropical
cyclone hazards in the context of epidemiological research. Further, we expand
on previous research that investigated methods to measure exposure to tropical
cyclones for epidemiological research~\parencite{grabich2015measuring}.  The
previous study investigated differences in which communities were assessed as
exposed to tropical cyclones during the 2004 hurricane season in Florida,
depending on whether exposure assessment was based on distance to the storm's
track or used a metric incorporating storm-related winds within the county
during the storm.  They found important differences across methods of assessing
storm exposure, concluding that a study may be prone to bias from exposure
misclassification if distance to the storm track is used as a proxy measurement
for exposure assessment~\parencite{grabich2015measuring}.  Here we expand to
investigate this question across all counties in states in the eastern half of
the \ac{US} over multiple storms and years.  Further, we investigate patterns
in exposure classification based on other metrics of storm-related
hazards---rainfall, flooding, and tornadoes---that are important to
characterize to improve understanding of the inland health impacts of tropical
cyclones~\parencite{czajkowski2011, moore2012}. These results can help
epidemiologists design studies and plan statistical analysis for multi-year,
multi-community studies that investigate changes in community-wide rates of
health outcomes during exposure to the hazards brought by tropical cyclones,
including counties inland from a storm's landfall.

### 2019-11-08 writing/ehp_methods.tex
Work some more on draft

\textit{We next investigated agreement between storm exposure
classifications based on these different single-hazard exposures, as well as
between each of these and a distance-based proxy assessment of tropical cyclone
exposure.} We calculated the within-storm
Jaccard index~\parencite{jaccard1901distribution, jaccard1908nouvelles} between
each pair of exposure metrics. The Jaccard index~($J_s$) measures similarity
between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical cyclone~$s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

>>>>

Next, we investigated how well exposure assessment agreed across 
these metrics. For each storm we investigated the degree to which the 
set of counties assessed as exposed based on one metric overlapped with the set
assessed as exposed based on each other metric, including a metric that used
distance of a county from the storm track as a proxy for exposure to storm hazards. 
We calculated the within-storm
Jaccard index ($J_s$)~\parencite{jaccard1901distribution, jaccard1908nouvelles} between
each pair of exposure metrics, which measures similarity
between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical cyclone~$s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

### 2019-11-08 writing/ehp_results.tex
Work some more on draft

\textit{We created and published this tropical cyclone exposure data as open-source
data, so they can be used by epidemiological
researchers~\parencite{hurricaneexposuredata}. These data include continuous
county-level measurements for the closest distance of each storm, cumulative
rainfall, and maximum sustained surface wind speed. These continuous metrics
can be used for classifying counties as exposed or unexposed, using thresholds
selected by the user, or can be used as continuous metrics. The dataset also
include binary data on flood and tornado events associated with each storm in
each county. To accompany these data, we published software tools to explore
and map the data and to integrate it with human health
datasets~\parencite{hurricaneexposure}.}

@@

For flood data, we compared the flood status values included in the open-source
data to streamflow measurements at \ac{US} Geological Survey gages within nine
sample counties (Figure~\ref{fig:floodcomparison}). Across the sampled
counties, streamgage data generally indicated higher discharge during periods
identified as flood events based on the NOAA Storm Events database,
particularly in counties with more reporting streamgages (e.g., Harris County,
TX, with~10 reporting stream gages; Figure~\ref{fig:floodcomparison}). There
were some cases, however, where the two flooding data sources were somewhat
inconsistent.  For example, there were one or two tropical cyclones in several
of the counties (Mobile County, AL, Escambia County, FL, and Montgomery County,
PA) with associated flood event listings but for which the total discharge
across county streamflow gages was relatively low. For storms without a flood
listing for the county, in most cases the total streamflow discharge in the
county was relatively low, and, in all but one of these cases all streamgage
flows were below the flooding threshold. The exception was for one storm in
Fulton County, GA (Hurricane Ida in 2009).

@@

We used this storm exposure data to classify counties as exposed or unexposed
to four different hazards for each tropical cyclone and then explored patterns
over years with available data. Across the four storm hazards considered, there
was wide variation in the average number of county exposures per year
(Table~\ref{tab:exposuresummaries}). For the tropical cyclone tornado exposure,
there were on average about 50 county exposures per year within our study.
County exposures were more frequent for tropical cyclone wind exposures ($>$140
/ yr on average), even more frequent for tropical cyclone flood exposures
($>$200 / yr on average), and most frequent for tropical cyclone rain exposure
($>$400 / yr on average).

\textit{We also measured the average number of counties exposed per storm to each
hazard (limiting this analysis to tropical cyclones that exposed at least one
county to that hazard; Table~\ref{tab:exposuresummaries}).  If a tropical
cyclone exposed any counties to tornadoes, it was typically only a few (median
counties exposed per storm:~7). When a storm exposed any counties to other
tropical cyclone exposures, the swath of exposed counties tended to be much
larger: a median of~25 counties exposed for high winds per storm,~26 for
flooding, and~68 for extreme rainfall.  For every hazard except tropical
cyclone tornadoes, we identified at least one tropical cyclone that exposed
over~250 counties (Table~\ref{tab:exposuresummaries}).  However, the
largest-extent tropical cyclone varied across hazards: Frances in~2004 exposed
the most counties based on rain, Ike in~2008 based on wind, and Ivan in 2004
based on flooding and tornadoes (Table~\ref{tab:exposuresummaries}).}

>>>>

We created and published this tropical cyclone exposure data as an R
package~\parencite{hurricaneexposuredata}.  The package size exceeded the
recommended maximum size for the standard repository for publishing R packages
(\ac{CRAN}). Therefore, we used the \textit{drat} framework to set up our own
repository to host the package~\parencite{anderson2017hosting}. These data
include continuous county-level measurements for the closest distance of each
storm, cumulative rainfall, and maximum sustained surface wind speed. These
continuous metrics can be used for classifying counties as exposed or
unexposed---using thresholds selected by the user---or can be extracted
directly as continuous metrics. The dataset also include binary data on flood
and tornado events associated with each storm in each county. To accompany
these data, we published an associated R package on \ac{CRAN} with software
tools to explore and map the data and to integrate it with human health
datasets~\parencite{hurricaneexposure}.

@@

For flood data, we compared the flood status values included in the open-source
data to streamflow measurements at \ac{US} Geological Survey gages within nine
sample counties (Figure~\ref{fig:floodcomparison}). Across the sampled
counties, streamgage data generally indicated higher discharge during periods
identified as flood events based on the NOAA Storm Events database,
particularly in counties with more reporting streamgages (e.g., Harris County,
TX, with~10 reporting stream gages; Figure~\ref{fig:floodcomparison}). There
were some cases, however, where the two flooding data sources were somewhat
inconsistent.  For example, there were one or two tropical cyclones in several
of the counties (Mobile County, AL, Escambia County, FL, and Montgomery County,
PA) with associated flood event listings but for which the total discharge
across county streamflow gages was relatively low. For storms without a flood
listing for the county, in most cases the total streamflow discharge in the
county was relatively low, and, in all but one of these cases all streamgage
flows were below the flooding threshold. The exception was for Hurricane Ida in
2009 in Fulton County, GA.

@@

We used this storm exposure data to classify counties as exposed or unexposed
to four different hazards for each tropical cyclone and then explored patterns
over years with available data. Across the four storm hazards considered, there
was wide variation in the average number of county exposures per year
(Table~\ref{tab:exposuresummaries}). For the tropical cyclone tornado exposure,
there were on average about 50 county exposures per year within our study.
County exposures were more frequent for tropical cyclone wind exposures ($>$140
/ yr on average), even more frequent for tropical cyclone flood exposures
($>$200 / yr on average), and most frequent for tropical cyclone rain exposure
($>$400 / yr on average). For every hazard except tornadoes, we identified at
least one tropical cyclone that exposed over~250 counties
(Table~\ref{tab:exposuresummaries}).  However, the largest-extent tropical
cyclone varied across hazards: Frances in~2004 exposed the most counties based
on rain, Ike in~2008 based on wind, and Ivan in 2004 based on flooding and
tornadoes (Table~\ref{tab:exposuresummaries}).
